A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-11-30 paper/paper.tex
paper: move stuff around

\section{Mathematical treatment of \texorpdfstring{$\nu$}{𝜈}-sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets, and \emph{semi-cubical} sets. We will proceed to explain the mathematical objects we have formalized.

@@

Hence, we need a coherence condition to commute the terms. Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section. These are by induction on the structure of $\framep$, $\layer$ and $\filler$. In particular, for $\cohl$, we need a $2$-dimensional coherence condition called $\coht$.

\subsection{Formal construction of \texorpdfstring{$\nu$}{nu}-sets}
% Abbreviated tables in this section
%
% The rule for implicit arguments for each table:
% show 1 explicit in first two parts
% show E + 1 explicit in the third part
\appendmask[bonak]{layer}[D]
\appendmask[bonak]{filler}[D]
\appendmask[bonak]{restrframe}[D]
\appendmask[bonak]{restrlayer}[D, d]
\appendmask[bonak]{restrfiller}[D, d]
\appendmask[bonak]{cohframe}[D]
\appendmask[bonak]{cohlayer}[D, d]
\appendmask[bonak]{cohfiller}[D, d]

@@

For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{appendix:A}.

@@

Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$. This is apriori undecidable, and we have to prove the commutation propositionally before using the reflection rule. Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$. This is what $\cohf$ proves, as shown in the table \ref{tab:coh}. Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.

@@

\section{Details on the mechanization}
\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}

\newpage
\appendix
\section{Tables in full detail\label{appendix:A}}
% Full tables in this section
%
% Clear the mask and label
\clearmask

@@

>>>>

\section{Semi-simplicial and semi-cubical sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets, and \emph{semi-cubical} sets. We will proceed to explain the mathematical objects we have formalized.

@@

Hence, we need a coherence condition to commute the terms. Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section. These are by induction on the structure of $\framep$, $\layer$ and $\filler$. Note that, for the construction in \ref{sec:itt}, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.

\subsection{Formal construction in extensional type theory}
% Abbreviated tables in this section
%
% The rule for implicit arguments for each table:
% show 1 explicit in first two parts
% show E + 1 explicit in the third part
\appendmask[bonak]{layer}[D]
\appendmask[bonak]{filler}[D]
\appendmask[bonak]{restrframe}[D]
\appendmask[bonak]{restrlayer}[D, d]
\appendmask[bonak]{restrfiller}[D, d]
\appendmask[bonak]{cohframe}[D]
\appendmask[bonak]{cohlayer}[D, d]
\appendmask[bonak]{cohfiller}[D, d]

@@

For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.

@@

Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$. This is apriori undecidable, and we have to prove the commutation propositionally before using the reflection rule. Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$. This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$. Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.

Note that in $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjuction of two equalities. Note also that in $\cohl$, we use the reflection rule to identify equality of functions with pointwise equality.

@@

\subsection{Formal construction in intensional type theory\label{sec:itt}}
We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will soon explain.

% Full tables in this section
%
% Clear the mask and label
\clearmask

@@

\subsection{Details on the mechanization}
\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}

Our formalization is done in the intensional type theory flavor of the calculus of inductive constructions. Working in intensional type theory necessitates explicitly supplying a number of type equalities, which hold definitionally in extensional type theory.
